---
title: "Street length and traffic intensity data validation"
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    toc_depth: 3
    self_contained: true
author: "Guido Schulz (guido.schulz@inwt-statistics.de)"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
---

```{r setup, message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
devtools::load_all()
library(dplyr)
library(ggplot2)
library(terra)
library(sf)

fig_width <- 12
fig_height <- 16

knitr::opts_chunk$set(
  echo = FALSE,
  fig.width = fig_width,
  fig.height = fig_height)
```

```{r, get_data}
strassenklassen <- c("0", "I", "II", "III", "IV", "V")

# Raw traffic (no of vehicles) data as vector data
traffic_sf <- extract_raw_clickhouse("traffic_raw") %>%
  st_transform(25833)
# Streets lines as vector data
streets_sf <- extract_raw_clickhouse("streets") %>%
  st_transform(25833)

# Streets lengths as df
sl_df <- send_query_clickhouse_out("traffic_intensity")
# Traffic intensity as df
ti_df <- send_query_clickhouse_out("validate_traffic_intensity")

# Convert into terra objects
streets_vect <- vect(streets_sf)
sl <- df_to_rast(sl_df)
ti <- df_to_rast(ti_df)
```

```{r, prepare_data}
sl_df_long <- sl_df %>%
  pivot_longer(
    cols = starts_with("strassenklasse"),
    names_to = "strassenklasse",
    names_prefix = "strassenklasse_",
    values_to = "length"
  ) %>%
  mutate(strassenklasse = factor(strassenklasse,
                                 levels = strassenklassen))
```

## Maps

### Original street lines

```{r}
ggplot() +
  geom_sf(data = streets_sf, aes(color = strassenklasse1)) +
  facet_wrap(~ strassenklasse1, ncol = 2) +
  coord_sf(datum = sf::st_crs(25833)) +
  theme(legend.position = "top")
```

### Calculated street lengths per cell

```{r}
plot(sl,
     nc = 2,
     maxcell = ncell(sl)) 
```

### Original traffic (number of vehicles)

#### Kfz

```{r}
ggplot() +
  geom_sf(data = traffic_sf, aes(color = kfz)) +
  coord_sf(datum = sf::st_crs(25833)) +
  theme(legend.position = "top")
```

#### Lkw

```{r}
ggplot() +
  geom_sf(data = traffic_sf, aes(color = lkw)) +
  coord_sf(datum = sf::st_crs(25833)) +
  theme(legend.position = "top")
```

### Traffic intensity per cell 

Interpretation of traffic intensity is:

* (= 1) traffic equals that of an average cell which has streets in it
* (< 1) less traffic than an average cell which has streets in it
* (> 1) more traffic than an average cell which has streets in it


```{r}
plot(ti,
     nc = 1,
     maxcell = ncell(ti))
```


##  Statistical distribution

### Street lengths per cell

```{r}
sl_df_long %>% 
  group_by(strassenklasse) %>% 
  summarise(as_tibble(rbind(summary(length))))
```

Here we can observe a very plausible lumping at 

* 50 (because cell size is 50m) and at 
* 100 (two streets passing through one cell either horizontally or vertically)

However, most cells have a street length of 0 for all street types - because
there are no streets in it. Plausible if we look at the maps above.

```{r, warnings = FALSE}
sl_df_long %>%
  ggplot(aes(x = length, y = "", color = strassenklasse)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(data = sl_df_long %>% filter(length > 0),
              alpha = 0.08,
              size = 0.004) +
  facet_wrap(~ strassenklasse,
              ncol = 1) +
  xlim(c(0, 130)) +
  theme(legend.position = "none",
        axis.title.y = element_blank())
```

### Traffic intensity

Interpretation of traffic intensity is:

* (= 1) traffic equals that of an average cell which has streets in it
* (< 1) less traffic than an average cell which has streets in it
* (> 1) more traffic than an average cell which has streets in it

#### Kfz

```{r}
summary(ti_df$traffic_intensity_kfz)
```
#### Lkw

```{r}
summary(ti_df$traffic_intensity_lkw)
```
